Eagle makes multi-locus association mapping on a genome-wide scale routine

### 2019-02-08 paper.tex
08Jan18 Nature Communications Submission Version 1
Just submitted to Bioinformatics

\title{Eagle: Making multi-locus association mapping on a genome-wide scale routine}
\author{Andrew W. George$^{1,*}$, Arunas Verbyla$^1$, Joshua Bowden$^2$}

@@

\begin{abstract}
We present Eagle, a new method for multi-locus association mapping. The motivation for developing Eagle was to make multi-locus association mapping "easy" and the method-of-choice. Eagle's strengths are that it a. is considerably more powerful than single-locus association mapping b. doesn't suffer from multiple testing issues c. is threshold free d. gives results that are immediately interpretable and e. has a computational footprint comparable to single-locus association mapping. By conducting a large simulation study, we will show that Eagle finds true and avoids false SNP-trait associations better than competing single- and multi-locus methods. We also analyse data from a published mouse study. Eagle found over two times more validated findings than the state-of-the-art single-locus method. Eagle has been implemented as an R package, with a web-based Graphical User Interface (GUI) for users less familiar with R.
\end{abstract}

>>>>

\title{Eagle makes multi-locus association mapping on a genome-wide scale routine}
\author{Andrew W. George$^{1,*}$, Arunas Verbyla$^1$, Joshua Bowden$^2$}

@@

\begin{abstract}
We present Eagle, a new method for multi-locus association mapping. The motivation for developing Eagle was to make multi-locus association mapping "easy" and the method-of-choice. Eagle's strengths are that it a. is considerably more powerful than single-locus association mapping b. doesn't suffer from multiple testing issues c. is threshold free d. gives results that are immediately interpretable and e. has a computational footprint comparable to single-locus association mapping. By conducting a large simulation study, we will show that Eagle finds true and avoids false SNP-trait associations better than competing single- and multi-locus methods. We also analyse data from a published mouse study. Eagle found over 100\% more validated findings than the state-of-the-art single-locus method. Eagle has been implemented as an R package, with a web-based Graphical User Interface (GUI) for users less familiar with R.
\end{abstract}
